Water Management

### 2020-02-22 Paper/paper.tex
Kleinere Anmerkungen

\subsubsection{Modification 3: Using Real Data for Rainfall}
Instead of simulating the rainfall with random numbers, we also use real data.
Comparing the results then allows us to draw conclusions on the accuracy of the simulation for that region. 
We use a dataset aquired from \citep{kaggle:2019}, that contains real rainfall data for the last 65 years in different regions of Bangladesh. % Zitation anpassen
% TODO describe how we fitted them to match the rainfall distribution

@@

A common technique to solve optimization or combinatorial problems is called Dynamic Programming. 
It is based on the idea of dividing problems into smaller subproblems, solving these recursively and caching intermediate results (\textit{memoization}). 
In his paper "The Theory Of Dynamic Programming" from 1957, Richard Bellman aimed to provide a solution to multi-stage-decision processes. 
He defines a \textit{policy} as "a sequence of decisions" (\cite{bellman:1957}, p.2), and an \textit{optimal policy} as "a policy, which is most advantageous according to some preassigned criterion" (\cite{bellman:1957}, p.2). 
This is reflected in Bellman's Principle of Optimality: "An optimal policy has the property that whatever initial state and initial decisions are, the remaining decisions must constitute an optimal policy with regard o the state resulting from the first decisions" (\cite{bellman:1957}, p.2).

@@

	\begin{equation}
s = \left( \begin{array}{c}0\\...\\7\end{array}\right),\hspace{2mm}x = \left( \begin{array}{c}0\\...\\7\end{array}\right)
\end{equation}

% TODO das scheint mir nicht so ganz korrekt zu sein. Meint ihr die Dimension?
Note that the maximum reservoir capacity is $7$ and $|s|=|x| = n = 1000$.

@@

which equals to finding the column $aux$ that maximizes the expected value over all states.
We repeat this step over and over again until the our value function $V$ converges.
In our case the function converges, if the norm of the difference between $V'$ and $V$ falls below a certain tolerance value) \\

@@

The water level found to be a steady state and the period in which this condition occurs changes from calculation to calculation due to the fact, that the rain fall is still a random distribution.

@@

To do so, we ran our code 1000 times and put the resulting water levels into bins with the size of 0.1 each.

@@

A small $\beta$ ensures that high water levels at the end of one period are only available to a small extent in the next period. 

>>>>

\subsubsection{Modification 3: Using Real Data for Rainfall}
Instead of simulating the rainfall with random numbers, we also use real data.
Comparing the results then allows us to draw conclusions on the accuracy of the simulation for that region. 
We use a dataset aquired from \citep{kaggle:2019}, that contains real rainfall data for the last 65 years in different regions of Bangladesh. % Zitation anpassen
To make this data fit our somewhat arbitrarily selected range of 0 to 7 for water levels in the reservoir, we...
% TODO describe how we fitted them to match the rainfall distribution

@@

A common technique to solve optimization or combinatorial problems is called Dynamic Programming. 
It is based on the idea of dividing problems into smaller subproblems, solving these recursively and caching intermediate results (\textit{memoization}). % Nicht eher "memoRization"?
In his paper "The Theory Of Dynamic Programming" from 1957, Richard Bellman aimed to provide a solution to multi-stage-decision processes. 
He defines a \textit{policy} as "a sequence of decisions" (\cite{bellman:1957}, p.2), and an \textit{optimal policy} as "a policy, which is most advantageous according to some preassigned criterion" (\cite{bellman:1957}, p.2). 
This is reflected in Bellman's Principle of Optimality: "An optimal policy has the property that whatever initial state and initial decisions are, the remaining decisions must constitute an optimal policy with regard to the state resulting from the first decisions" (\cite{bellman:1957}, p.2).

@@

	\begin{equation}
s = \left( \begin{array}{c}0\\...\\7\end{array}\right),\hspace{2mm}x = \left( \begin{array}{c}0\\...\\7\end{array}\right)
\end{equation}
% TODO Gibt es hier nicht eine mathematisch schönere Schreibweise um einen Vektor mit 1000 Einträgen darzustellen? (R hoch 1000/ R hoch n)
% TODO das scheint mir nicht so ganz korrekt zu sein. Meint ihr die Dimension?
Note that the maximum reservoir capacity is $7$ and $|s|=|x| = n = 1000$.

@@

which equals to finding the column $aux$ that maximizes the expected value over all states.
We repeat this step over and over again until the our value function $V$ converges.
In our case the function converges, if the norm of the difference between $V'$ and $V$ falls below a certain tolerance value \\

@@

The water level found to be a steady state and the period in which this condition occurs changes from calculation to calculation due to the fact, that the rainfall is still a random distribution.

@@

To do so, we ran our code 1000 times and put the resulting water levels into bins with the size of 0.1 each. % "the forward simulation" instead of "our code"?

@@

A small $\beta$ ensures that high water levels at the end of one period are only available to a small extent in the next period. % Finde die Formulierung nicht so gut: Sie sind ja weiterhin voll verfügbar, aber eben in Zukunft weniger wert. Bzw das könnte man diskutieren.
